Critical Temperature of YBCO and BSCCO Superconductors

### 2014-12-04 Draft.tex
first half of comments on results

First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the Teachspin manual that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig. \ref{TCplot}). While it was best fit piecemeal, a single curve was able to cover our temperature range, and we used that function to convert our thermocouple voltages in later fits.

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: Plot of Temperature and thermocouple voltage transcribed from the Teachspin manual, with fit lines across different sections.}
\label{TCplot}
\end{figure}

We gathered data across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig. \ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig. \ref{YBCOplot2}). In order to determine the critical temperature, we found the point along the transition period that was exactly in between the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines. This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.

>>>>

First, to convert our thermocouple voltage into a usable temperature, we transcribed the chart provided in the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} that came with the YBCO and BSCCO samples and and plotted temperature vs voltage (see Fig. \ref{TCplot}). While it was best fit piecemeal, a single curve was able to cover our temperature range, and we used that function to convert our thermocouple voltages in later fits.

\begin{figure}[h!]
\centering
\includegraphics[width=7in]{thermocouple_voltage_vs_temp.png}
\caption{Figure 1: \textcolor{blue}{PROOFREAD!} Plot of Temperature and thermocouple voltage transcribed from the \textcolor{red}{Teachspin manual}\textcolor{green}{Colorado Superconductor Inc} , with fit lines across different sections.}
\label{TCplot}
\end{figure}

We gathered data across two warm-ups of the YBCO sample, the first at equal time intervals between points (see Fig. \ref{YBCOplot1}) and the second focusing on taking more points during the transition period than elsewhere (see Fig. \ref{YBCOplot2}).

In order to determine the critical temperature, we found the point along the transition period that was \textcolor{red}{exactly in between}\textcolor{blue}{do you mean halfway between?} the trend line for resistance during non-superconductivity and the trend line for resistance during superconductivity, and noted the corresponding temperature. The error in our voltage readings was very low (on the order of 0.000005mV), so the larger element of error is looking at the width of the transition zone, which was defined between the first points to clearly deviate from the trend lines. This yielded results of a $T_C$ of 98.03K and 98.67K per trial, with a range of 91K to 100K and 94K to 101K, respectively.

\textcolor{blue}{does this mean your first transition occurs at }$T_C = 98.0 \pm 4.5 \textrm{ K}$ \textcolor{blue}{ or that the transition begins at 91 K, ends at 100 K, and has a midpoint at 98 K? If the latter, what do you take to be the uncertainty in your determination of that midpoint? }
